\documentclass[12pt,letterpaper,boxed]{hmcpset}

\usepackage[margin=1in]{geometry}

\usepackage{graphicx}

\usepackage{enumitem}
\usepackage{amsmath}

\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 12f}
\duedate{04/13/2018}

\begin{document}

\problemlist{12.3.13, 12.3.16, 16.1.9, 16.1.10, 16.1.20}

\begin{problem}[12.3.13]
Let $G$ be a group of order 30. Show that $G$ has a normal Sylow 3-subgroup $\textit{and}$ a normal Sylow 5-subgroup. 
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[12.3.16]
Let $G$ be a group of order $455 = 5 \times 7 \times 13$.
\begin{enumerate}[label=\alph*]
\item What are the possibilities for $\vert \text{Syl}_5(G) \vert$, $\vert \text{Syl}_7(G) \vert$, $\vert \text{Syl}_{13}(G) \vert$?
\item Can $G$ be simple?
\item How many elements of order 13 does $G$ have?
\item Let $P \in \text{Syl}_{13}(G)$ and $Q \in \text{Syl}_5(G)$. Is $PQ$ necessarily a group? Why? Assume that $PQ$ is a group, then what are the possibilities for $\vert \textbf{Z}(PQ) \vert$?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[16.1.9]
The elements of the set $\mathbb{Z}_{(5)}$ are rational numbers. A rational number $q$ is in the set $\mathbb{Z}_{(5)}$ if and only if $q$ can be written as $a/b$ where $a$ and $b$ are integers, gcd($a$,$b$) = 1, and $b$ is not divisible by 5. Is $\mathbb{Z}_{(5)}$ a ring? Is it a field? Can you find a non-trivial ideal of $\mathbb{Z}_{(5)}$? If the answer is yes, explicitly construct such an ideal, and if the answer is no, give a reason.
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[16.1.10]
Let $R = \mathbb{Q}[\sqrt{2}]$ and $S = \mathbb{Q}[\sqrt{3}]$. Show that the only ring homomorphism from $R$ to $S$ is the trivial one. In particular, conclude that $R$ and $S$ are not isomorphic rings. In other words, assume $f : R \rightarrow S$ is a ring homomorphism. Show that $f(r) = 0$ for all $r \in R$.
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[16.1.20]
Let $R$ be a ring with identity, and let $J$ be an ideal of $R$. Assume that $J$ contains a unit of $R$. Prove that $J = R$.
\end{problem}

\begin{solution}

\end{solution}

\end{document}