\documentclass[12pt,letterpaper,boxed]{hmcpset}

\usepackage[margin=1in]{geometry}

\usepackage{graphicx}

\usepackage{enumitem}
\usepackage{amsmath}

\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 14f}
\duedate{04/27/2018}

\begin{document}

\problemlist{18.2.6, 18.3.13, 18.4.6, 18.6.1, 18.6.2}

\begin{problem}[18.2.6]
Let $C[0,1] = \{f:[0,1] \rightarrow \mathbb{R} \vert f \text{is continuous}\}$ denote the ring of real valued continuous functions with pointwise addition and multiplication $((f+g)(x) = f(x)+g(x)$ and $(fg)(x) = f(x)g(x)$. 
\begin{enumerate}[label=\alph*]
\item Let $0 \leq a \leq b \leq 1$ be real numbers, and define $J = \{ f\in C[0,1] \vert f(x) = 0 \text{for} a \leq x \leq b\}$. Is $J$ an ideal of $C[0,1]$?
\item Is $C[0,1]$ noetherian?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.3.13]
Let $$R = \{p \in \mathbb{Q}[x] \vert p(0) \in \mathbb{Z}\}.$$
In other words, $R$ consists of those polynomials with rational coefficients whose constant terms is an integer.
\begin{enumerate}[label=\alph*]
\item Is $R$ an integral domain?
\item What are the units of $R$?
\item Is $x$ irreducible in $R$? Is $x$ a product of irreducibles? Why?
\item Is $x$ prime in $R$? Is $R$ a UFD? Why?
\item What are the elements of $\langle x \rangle$? Describe them explicitly.
\item What are the elements of $R/\langle x \rangle$? Can you find an explicit zero divisor in this ring?
\item Is $R$ noetherian? Why?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.4.6]
Let $R = \mathbb{Z}[i]$, and for $x \in R$, define $d(x) = N(x)$ where $N(x)$ is the norm of $x$ (Definition 18.23 page 375).
\begin{enumerate}[label=\alph*]
\item For $x,y \in R - \{0\}$, show that $d(x) \leq d(xy)$.
\item For the following values of $x$ and $y$ find $q$ and $r$ such that $x = yq+r$, and either $r = 0$ or $d(r) < d(y)$:
\begin{enumerate}
\item $x = 10i$, $y = 5+3i$.
\item $x = 5+11i$, $y = 2+8i$.
\end{enumerate}
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.6.1]
Let $R$ be a non-trivial commutative ring with identity. Show that the following are equivalent:
\begin{enumerate}[label=\alph*]
\item $R$ is local.
\item The set of all non-unis of $R$ forms an ideal of $R$.
\item The sum of any two non-units of $R$ is a non-unit.
\item If $x \in R$, then $x$ or $1-x$ is a unit.
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.6.2]
Let$R$ be a local commutative ring with identity, and assume that the maximal ideal in $R$ is a principal ideal. Let $a$ be an irreducible element of $R$. Show that $\langle a \rangle$ is maximal.
\end{problem}

\begin{solution}
\end{solution}

\end{document}