\documentclass[12pt,letterpaper,boxed]{hmcpset}

\usepackage[margin=1in]{geometry}

\usepackage{graphicx}

\usepackage{enumitem}
\usepackage{amsmath}

\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 14w}
\duedate{04/25/2018}

\begin{document}

\problemlist{18.1.21, 18.1.24, 18.1.29, 18.2.5, 18.3.13}

\begin{problem}[18.1.21]
Let $R = \mathbb{Z}[\sqrt{-5}]$.
\begin{enumerate}[label=\alph*]
\item Find all units of $R$.
\item Is $1 + \sqrt{-5}$ irreducible in $R$?
\item Is 2 a prime in $R$?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.1.24]
Let $I = \{(2m,3n) \vert m,n \in \mathbb{Z}\}$. Verify that $I$ is an ideal in $\mathbb{Z} \times \mathbb{Z}$. Is this ideal principal, prime, and/or maximal?
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.1.29]
Let $f = x^2 + x + 1$.
\begin{enumerate}[label=\alph*]
\item Is the ring $\mathbb{F}_7[x]/\langle f \rangle$ an integral domain?
\item Show that $\mathbb{Z}[x]/\langle 7 \rangle \cong \mathbb{F}_7[x]$.
\item Is $\langle f,7 \rangle $ a maximal ideal of $\mathbb{Z}[x]$? Is it a prime ideal?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.2.5]
Let $K$ be a field, and let $R = K[x_1,x_2,...]$ be the ring of polynomials in an infinite sequence of variables over the field $K$. (The elements of $R$ are polynomials with a finite number of terms, but the number of variables is infinite.)
\begin{enumerate}[label=\alph*]
\item Convince yourself that $R$ is an integral domain.
\item Is $R$ noetherian?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.3.13]
Let $$R = \{p \in \mathbb{Q}[x] \vert p(0) \in \mathbb{Z}\}.$$
In other words, $R$ consists of those polynomials with rational coefficients whose constant terms is an integer.
\begin{enumerate}[label=\alph*]
\item Is $R$ an integral domain?
\item What are the units of $R$?
\item Is $x$ irreducible in $R$? Is $x$ a product of irreducibles? Why?
\item Is $x$ prime in $R$? Is $R$ a UFD? Why?
\item What are the elements of $\langle x \rangle$? Describe them explicitly.
\item What are the elements of $R/\langle x \rangle$? Can you find an explicit zero divisor in this ring?
\item Is $R$ noetherian? Why?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\end{document}