\documentclass[12pt,letterpaper,boxed]{hmcpset}

\usepackage[margin=1in]{geometry}

\usepackage{graphicx}

\usepackage{enumitem}
\usepackage{amsmath}

\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 15m}
\duedate{04/30/2018}

\setlength\parindent{1.5cm}

\begin{document}

\problemlist{18.2.5, 18.3.9, 18.4.1, 18.4.6, 18.6.4}

\begin{problem}[18.2.5]
Let $K$ be a field, and let $ R = K[x_1,x_2,...] $ be the ring of polynomials in an infinite sequence of variables over the field $K$. (The elements of $R$ are polynomials with a finite number of terms, but the number of variables is infinite.)
\begin{enumerate}[label=\alph*]
\item Convince yourself that $R$ is an integral domain.
\item Is $R$ noetherian?  
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.3.9]
Can 5 be factored uniquely in $\mathbb{Z}[\sqrt{-6}]$? Is $\mathbb{Z}[\sqrt{-6}]$ a UFD?
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.4.1]
$\textbf{Proof of Lemma 18.55.}$ Let $D$ be a Euclidean domain with degree function $d$. Assume $u \in D$. Show that $u$ is a unit if and only if $d(u) = d(1)$.
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.4.6]
Let  $R = \mathbb{Z}[i]$, and for $x \in R$, define $d(x) = N(x)$ where $N(x)$ is the norm of $x$ (Definition 18.23 page 375).
\begin{enumerate}[label=\alph*]
\item For $x,y \in R - \{0\}$, show that $d(x) \leq d(xy)$.
\item For the following values of $x$ and $y$ find $q$ and $r$ such that $x = yq+r$, and either $r=0$ or $d(r) < d(y)$:
\newline
\indent (i) $ x = 2+10i, y = 5+3i$.
\newline
\indent (ii) $x = 5+11i, y = 2+8i$.
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[18.6.4]
Consider $\mathbb{Z}$, the ring of integers, and let $M = \mathbb{Z} - \langle 47 \rangle$. Define $\mathbb{Z}_{(47)}$ to be $\mathbb{Z}[M^{-1}]$, the localization of $\mathbb{Z}$ at $M$ (see Definition 17.9).
\begin{enumerate}[label=\alph*]
\item Convince yourself that this definition of $\mathbb{Z}_{(47)}$ is consistent with the one in Example 18.79.
\item What are the units of $\mathbb{Z}_{(47)}$? What is char$(\mathbb{Z}_{(47)})$? Is $47 \in \mathbb{Z}_{(47)}$? What is the field of fractions of $\mathbb{Z}_{(47)}$?
\item Let $I$ be the ideal generated by 47 in $\mathbb{Z}$, and let $J$ be the ideal generated by 47 in $\mathbb{Z}_{(47)}$. Is $I=J$? Describe the elements of $I$ and $J$.
\item Let $x \in \mathbb{Z}_{(47)} - J$. Is $x$ invertible in $\mathbb{Z}_{(47)}$? Use your answer to prove that $J$ is a maximal ideal in $\mathbb{Z}_{(47)}$. Does $\mathbb{Z}_{(47)}$ have any other maximal ideals?
\item Is 47 a prime in $\mathbb{Z}_{(47)}$? Apart from 47 and its associates, are there any other primes in $\mathbb{Z}_{(47)}$?
\item is $\mathbb{Z}_{(47)}$ a DVR?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}


\end{document}