% HMC Math dept HW template example
% v0.04 by Eric J. Malm, 10 Mar 2005
\documentclass[12pt,letterpaper,boxed]{hmcpset}

% set 1-inch margins in the document
\usepackage[margin=1in]{geometry}

% include this if you want to import graphics files with /includegraphics
\usepackage{graphicx}

% info for header block in upper right hand corner
\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 2m}
\duedate{01/22/2018}

\begin{document}

\problemlist{1.2.4, 1.2.6, 1.2.15, 1.2.20, 1.3.1}

\begin{problem}[1.2.4]
Let $ \sigma  = (1 \ 3 \ 4)(2 \ 4)$ and $ \tau = (1 \ 5)(2 \ 3)$ be elements of $S_5$. Find $\sigma^2$, $\sigma\tau$, $\tau\sigma$, and $\tau\sigma^2$
\end{problem}

\begin{solution}

\end{solution}

\clearpage

\begin{problem}[1.2.6]
Let $ f = (1 \ 2 \ 3) \in S_3 $. Find the maps in the following sequence $$ 1_{[3]}, f, f^2, f^3, f^4, f^5, \cdots $$. Do you see a pattern?
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[1.2.15]
\begin{itemize}
  \item[(\textit{a})] Give an example of a map $ f $ that has a right inverse, but not an inverse. 
  
  \item[(\textit{b})] Show that $ f $ has a right inverse if and only if $ f $ is onto. 
\end{itemize}
\end{problem}

\begin{solution}
\end{solution}

\clearpage


\begin{problem}[1.2.20]
Let $ S $ be a set with a finite number of elements, and let $ f: S \to S $ be a map.
\begin{itemize}
  \item[(\textit{a})] If $ f $ is onto, can $ f $ not be 1-1?
  
  \item[(\textit{b})] If $ f $ is 1-1, can $ f $ not be onto? 
  
  \item[(\textit{c})] Do your conclusions remain valid even if $ S $ has an infinite number of elements?
\end{itemize}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[1.3.1]
\begin{itemize}
  \item[(\textit{a})] If $ f $ is onto, can $ f $ not be 1-1?
  
  \item[(\textit{b})] In $ \mathbb{Z}/12\mathbb{Z} $ does every non-zero element have a multiplicative inverse (i.e., for $ a \in \mathbb{Z}/12\mathbb{Z} $, can we find $ b $ such that $ ab = 1 $)?
  
  \item[(\textit{c})] In $ \mathbb{Z}/7\mathbb{Z} $ does every non-zero element have a multiplicative inverse? 
  
  \item[(\textit{d})] We want to know for which integers $ n > 1 $ every non-zero element of $ \mathbb{Z}/n\mathbb{Z} $ has a multiplicative inverse. Look at some examples and make a conjecture. You do not have to prove your conjecture. 
\end{itemize}
\end{problem}

\begin{solution}

\end{solution}

\end{document}
