% HMC Math dept HW template example
% v0.04 by Eric J. Malm, 10 Mar 2005
\documentclass[12pt,letterpaper,boxed]{hmcpset}

% set 1-inch margins in the document
\usepackage[margin=1in]{geometry}

% include this if you want to import graphics files with /includegraphics
\usepackage{graphicx}

% info for header block in upper right hand corner
\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 3f}
\duedate{02/02/2018}

\begin{document}

\problemlist{2.3.16, 2.3.19, 2.3.21, 2.4.6, 2.5.3}

\begin{problem}[2.3.16]
Let $G$ be a group, and let $x,y \in G$. Assume that $xy = yx$, $o(x) = p$, and $o(y) = q$, where $p$ and $q$ are distinct prime numbers. What can you say about $o(xy)$?
\end{problem}

\begin{solution}

\end{solution}

\clearpage

\begin{problem}[2.3.19]
\begin{itemize}
  \item[(\textit{a})] Let $G = \{e, a,...,a^9 \vert a^{10} = e\} $ be the cyclic group of order 10. For which $m$ is $G = \langle a^m \rangle$?
  
  \item[(\textit{b})] Let $G = \langle g \rangle$ be a cyclic group of order $n$.  For which $m$ is $g^m$ a generator of $G$? Why?
\end{itemize}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[2.3.21]
Consider a fixed shuffle of a deck of cards. Does repeating this fixed shuffle some finite (positive) number of times bring the deck eventually back to its original order? Why? 
\end{problem}

\begin{solution}
\end{solution}

\clearpage


\begin{problem}[2.4.6]
Recall that $G$ = GL(2,$\mathbb{R}$) is the group of all invertible 2 $\times$ 2 matrices with entries in the reals $\mathbb{R}$. 
\begin{itemize}
  \item[(\textit{a})] We want to see if inside $G$ there is a group isomorphic to $D_8$. In other words, can we find a group isomorphic to $D_8$ consisting of 2 $\times$ 2 invertible matrices with real entries? \newline Let $S$ be the square in $\mathbb{R}^2$ with vertices at ($\pm$1,$\pm$1). Think of elements of $D_8$ as linear transformations from $\mathbb{R}^2$ to $\mathbb{R}^2$. For example $a$ is the linear transformation that rotates every vector 90 $\deg$. Find a 2 $\times$ 2 matrix for each of these linear transformations. Do they form a group isomorphic to $D_8$?
  
  \item[(\textit{b})] Can you find a group isomorphic to $D_8$ consisting of elements of GL(2,$\mathbb{C}$)?
  
  \item[(\textit{c})] Can you find a group isomorphic to $D_8$ consisting of elements of GL(2,3)?
\end{itemize}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[2.5.3]
Does there exist a non-cyclic group of order 99? If the answer is yes, then find two non-isomorphic groups of order 99. 
\end{problem}

\begin{solution}

\end{solution}

\end{document}
