\documentclass[12pt,letterpaper,boxed]{hmcpset}

% set 1-inch margins in the document
\usepackage[margin=1in]{geometry}

% include this if you want to import graphics files with /includegraphics
\usepackage{graphicx}

% info for header block in upper right hand corner
\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 3m}
\duedate{01/29/2018}

\begin{document}

\problemlist{1.4.9, 2.1.8, 2.2.1, 2.2.4, 2.3.1}

\begin{problem}[1.4.9]
$\textbf{The size of}$ SL($n$,$p$). For this problem, accept as given that det($AB$) = det($A$)det($B$) for $n \times n$ matrices $A$ and $B$, and that a matrix (with entries in a field) is invertible if and only if its determinant is non-zero. Let $M$ be an arbitrary matrix in GL($n$,$p$). 
\begin{itemize}
  \item[(\textit{a})] How many possible choices are there for det($M$)?
  
  \item[(\textit{b})] Let $k$ be an arbitrary non-zero element of $\mathbb{Z}/p\mathbb{Z}$. Give an explicit $n \times n$ matrix $A$ with det($A$) = $k$.
  
  \item[(\textit{c})] Let $\alpha$ and $\beta$ be non-zero elements of $\mathbb{Z}/p\mathbb{Z}$. Let $S_1$ be the set of elements of GL($n$,$p$) with determinant equal to $\alpha$. Likewise, let $S_2$ = {$M \in$ GL($n$,$p$) $\vert$ det($M$) = $\beta$}. Let $A$ be an $n \times n$ matrix with determinant equal to $\beta/\alpha$. Prove that the map $f: S_1 \to S_2$ defined by $f(N) = AN$ is an actual 1-1, onto function. Conclude that $|S_1| = |S_2|$.
  
  \item[(\textit{d})] Prove the statement about $|SL(n,p)|$ in Theorem 1.64. 
\end{itemize}
\end{problem}

\begin{solution}

\end{solution}

\clearpage

\begin{problem}[2.1.8]
Let $ G $ be a group of functions from a set $S$ to itself with multiplication defined as function composition. Find an example with $|G| \geq 2$ such that $G$ does not contain any 1-1 functions. 
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[2.2.1]
Let $G$ be a group. Prove that $(ab)^{-1} = a^{-1}b^{-1}$ for all $a$ and $b$ in $G$ if and only if $G$ is abelian. 
\end{problem}

\begin{solution}
\end{solution}

\clearpage


\begin{problem}[2.2.4]
\begin{itemize}
  \item[(\textit{a})] If $G$ is a finite group of even order, show that there must be an element $a \neq e$, such that $a^{-1} = a$.
  
  \item[(\textit{b})] Give an example to show that the conclusion of part (a) above does not hold for groups of odd order. 
\end{itemize}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[2.3.1]
Find the order of each of the elements of the following groups: $\mathbb{Z}/12\mathbb{Z}$, $S_3$, and GL(2,2).
\end{problem}

\begin{solution}

\end{solution}

\end{document}
