\documentclass[12pt,letterpaper,boxed]{hmcpset}

\usepackage[margin=1in]{geometry}

\usepackage{graphicx}

\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 5m}
\duedate{02/12/2018}

\begin{document}

\problemlist{2.6.23, 4.3.3, 4.4.7, 4.4.9, 4.4.16}

\begin{problem}[2.6.23]
Let $n$ be an integer bigger than 1, and let $\phi(n)$ be the Euler totient function. Use Problems $\textbf{2.6.22}$ and 2.3.20 to show $$ \sum_{d \vert n} \phi(d) = n. $$
\end{problem}

\begin{solution}

\end{solution}

\clearpage

\begin{problem}[4.3.3]
Let $ G = D_8 $, $ H = \langle b \rangle $, and $ K = \langle a^2 \rangle $. Find $ \textbf{N}_G(H) $ and $ \textbf{N}_G(K) $.
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[4.4.7]
Let a group $G$ act on itself by the conjugation action. What is the significance of conjugacy classes consisting of one element?
\end{problem}

\begin{solution}
\end{solution}

\clearpage


\begin{problem}[4.4.9]
We have a group $ G = \{ x_1,x_2,\cdots,x_8 \} $ with eight elements and a set $\Omega = \{ 1,2,3,4,5,6,7,8 \} $ also with eight elements. We know that $G$ acts on $\Omega$. As usual, the action of every group element can be described by a permutation of elements of $\Omega$. We are told that these permutations are as follows. $$ x_1 \mapsto 1, $$ $$ x_2 \mapsto 1, $$ $$ x_3 \mapsto (2 \ 4)(6 \ 8), $$ $$ x_4 \mapsto (2 \ 4)(6 \ 8), $$ $$ x_5 \mapsto (5 \ 7)(6 \ 8), $$ $$ x_6 \mapsto (5 \ 7)(6 \ 8), $$ $$ x_7 \mapsto (2 \ 4)(5 \ 7), $$ $$ x_8 \mapsto (2 \ 4)(5 \ 7). $$
\begin{itemize}
  \item[(\textit{a})] What is Stab$_G$(2)?
  
  \item[(\textit{b})] What is $ \mathcal{O}_{\Omega} $(2)?
  
  \item[(\textit{c})] Find two subgroups of order 4 in $G$. Explain how you got them. 
  
  \item[(\textit{d})] Find a subgroup of order 2 in $G$, and explain how you found it. 
  
  \item[(\textit{e})] Assume that $ S = \{ x_3,x_5 \} $ is a set of generators for $G$. Draw the Cayley diagraph of the action of $G$ on $\Omega$ with respect to $S$.
\end{itemize}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[4.4.16]
Find the number of conjugacy classes of $S_4$ and the number of elements in each of these classes. 
\end{problem}

\begin{solution}

\end{solution}

\end{document}
