\documentclass[12pt,letterpaper,boxed]{hmcpset}

\usepackage[margin=1in]{geometry}

\usepackage{graphicx}

\usepackage{enumitem}
\usepackage{amsmath}

\name{Daniel Bashir}
\class{Math 171}
\assignment{Homework 8w}
\duedate{03/07/2018}

\begin{document}

\problemlist{10.2.11, 10.2.15, 10.2.21, 10.3.1, 10.3.3}

\begin{problem}[10.2.11]
Let $ G = D_{34} = \langle a,b \ \vert \ a^{17} = b^2 = e, ba = a^{16}b \rangle $. 
\begin{enumerate}[label=\alph*]
\item Draw a partial lattice diagram of subgroups of $G$ that includes the subgroups $H$ and $K$. Include also $ H \cap K$ and $ \langle H,K \rangle $. Label the edges  with appropriate numbers, and give reasons for what you have done. \newline In what follows, you may refer back to your diagram. 
\item Is $ H \triangleleft G $? What is $ \textbf{N}_G(H) $? What is $ \textbf{N}_G(K) $? Why? is $ K \triangleleft G $?
\item What is $ \vert $ cl$_G(a) \vert $? What is $ \vert $ cl$_G(b) \vert$? Why? Note that cl$_G(x)$ is the conjugacy class of $x$ in $G$. 
\item What is $\textbf{Z}(G)$? Why?
\end{enumerate}
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[10.2.15]
$\textbf{Proof of Proposition 10.18(g).}$ Let $N$ be a subgroup of $G$. Prove that $N$ is normal if and only if $N$ is the union of some of the conjugacy classes of $G$. 
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[10.2.21]
$\textbf{Proof of Theorem 10.23.}$ $G$ is a group. $M \triangleleft G$ and $N \triangleleft G$. Assume $M \cap N = \{ e \}$. Show that for all $m \in M$ and $n \in N$, we have $mn = nm$. Does this mean that $G$ is abelian?
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[10.3.1]
Let $ G = S_4 $ and let $ K = \{ 1,(1 \ 2)(3 \ 4),(1 \ 3)(2 \ 4),(1 \ 4)(2 \ 3) \} $. $K$ is a normal subgroup of $G$. What is the order of $G/K$? Which group is $G/K$ isomorphic to? 
\end{problem}

\begin{solution}
\end{solution}

\clearpage

\begin{problem}[10.3.3]
Let $G = \mathbb{Z} / 4\mathbb{Z} \times \mathbb{Z} / 6 \mathbb{Z} $, and let $H$ be the subgroup of $G$ generated by (2,2). 
\begin{enumerate}[label=\alph*]
\item What are the elements of $H$?
\item What are the elements of $G/H$?
\item Find a familiar group that is isomorphic to $G/H$.
\end{enumerate}
\end{problem}

\begin{solution}

\end{solution}

\end{document}